PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-08-24 paper/paper.tex
reverted paper.tex
Abstract and introduction

\title{PineAPPL:\\ combining EW and QCD corrections for PDF fits}

@@

\abstract{We introduce \textsc{PineAPPL}, a library that produces
  fast-interpolation grids of physical cross sections, computed with a 
  general-purpose Monte Carlo generator, accurate to fixed order in the
  strong, electroweak, and combined strong-electroweak couplings. We
  discuss its features in comparison to similar software
  available in the literature, and we explicitly interface it to
  \textsc{MadGraph5\_aMC@NLO}. We validate the performance of \textsc{PineAPPL}
  by computing fast-interpolation grids, accurate to next-to-leading order in
  the strong and electroweak couplings, for a representative set of processes
  commonly used in the determination of the parton distribution functions (PDFs)
  of the proton. We formulate a recommendation on the format of the experimental
  deliverables in order to consistently incorporate them in forthcoming
  fits of PDFs including electroweak corrections.}

>>>>

\title{PineAPPL: combining EW and QCD corrections\\
  for fast evaluation of LHC processes}

@@

\abstract{We introduce \textsc{PineAPPL}, a library that produces
  fast-interpolation grids of physical cross sections, computed with a 
  general-purpose Monte Carlo generator, accurate to fixed order in the
  strong, electroweak, and combined strong-electroweak couplings. We
  discuss its features in comparison to similar software
  available in the literature, and we explicitly interface it to
  \textsc{MadGraph5\_aMC@NLO}. We validate the performance of \textsc{PineAPPL}
  by computing fast-interpolation grids, accurate to next-to-leading order in
  the strong and electroweak couplings, for a representative set of LHC
  processes for which EW corrections may have a sizeable effect on the accuracy
  of the corresponding theoretical predictions.
  We formulate a recommendation on the format of the experimental
  deliverables in order to consistently compare them with computations
  that incorporate EW corrections.}
